---
title: "Final_Project_Draft"
author: "Jake Peters & Soka"
date: "4/20/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(caret)
library(ISLR2)
library(lubridate)
library(scales)
library(tidytext)
library(textdata)
library(broom)
library(dslabs)
library(stringi)
```

```{r}
df_tweets <- read_csv("https://raw.githubusercontent.com/aksoralis/Data-Mining/main/tweets_EST.csv")
stocks <- read_csv("https://raw.githubusercontent.com/aksoralis/Data-Mining/main/stocksdf.csv")
tweets <- df_tweets %>% select(tweet, link, replies_count, likes_count, retweets_count, date)
tweets <- tweets %>% mutate(Date = as.Date(date))
clean <- left_join(tweets,stocks, by= "Date")
clean <- clean %>% 
           filter(Date >= ymd("2017-11-10"))
clean <- clean %>% distinct(link, .keep_all = TRUE)
```

```{r}
utf <- clean %>%
    mutate_at(vars(tweet), function(x){gsub('[^ -~]', '', x)}) #what is this doing?
tweet_words <- utf %>% 
  unnest_tokens(word, tweet, token = "tweets")

tweet_words %>% 
  count(word) %>%
  arrange(desc(n))
```

taking all stop words out
```{r}
tweet_words <- utf %>% 
  unnest_tokens(word, tweet, token = "tweets") %>%
  filter(!word %in% stop_words$word ) 

tweet_words %>% 
  count(word) %>%
  top_n(400, n) %>%
  mutate(word = reorder(word, n)) %>%
  arrange(desc(n))
```


tesla words: tesla, @tesla, car, production, @teslarati, cars, engine, @thirdrowtesla, future, power, energy, engines, electric, engineering, autopilot, drive, range, ai, factory, speed, computer, fast, rate, product, battery, control, selfdriving, vehicle, @teslagong, cybertruck, improvements, driving, hardware, testing, data, @teslatruth, gas, @tesmaniancom, reusable, road, fuel, move, mode, vehicles, moving, sustainable, traffic, faster

```{r}
# tesla score values
tweet_words_TF <- tweet_words %>% mutate(word_in_tesla = word %in% c("tesla","@teslaownerssv", "@tesla", "car", "production", "@teslarati", "cars", "engine"," @thirdrowtesla", "future", "power", "energy", "engines", "electric", "engineering", "autopilot", "drive", "range", "ai", "factory", "speed", "computer", "fast"," rate", "product", "battery", "control", "selfdriving", "vehicle", "@teslagong", "cybertruck", "improvements", "driving", "hardware", "testing", "data", "@teslatruth", "gas", "@tesmaniancom", "reusable", "road", "fuel", "move", "mode", "vehicles", "moving", "sustainable", "traffic", "faster"))
tfcount <- tweet_words_TF %>% group_by(link) %>% summarize(tesla_score = sum(word_in_tesla)) %>%
  ungroup()
scored <- left_join(utf, tfcount, by = "link")
```

tweet sentiment values
```{r}
 afinn <- get_sentiments("afinn") %>%
  select(word, value)
sentiment_counts <- tweet_words %>%
  left_join(afinn, by = "word") %>% filter(value != "NA")
# add up sentiments for each tweet
sentiment_sum <- sentiment_counts %>% group_by(link) %>% summarize(sentiment_score = sum(value)) %>% ungroup()
scored_tesla_and_sentiments <- left_join(scored, sentiment_sum, by = "link")
```

```{r}
# write.csv(scored_tesla_and_sentiments, "C:/Users/13204/Documents/Data Mining/Final_Project/DATA318 Final Project/scored_tesla_and_sentiments.csv", row.names = FALSE)
```

```{r}
data <- scored_tesla_and_sentiments
set.seed(51)
data <- data %>% filter(!is.na(teslaDiff.p))
test_index <- createDataPartition(data$teslaDiff.p, p = 0.20, list = FALSE)
test_set <- data[test_index,]
train_set <- data[-test_index,]

lm.mod <- lm(teslaDiff.p ~ tesla_score + sentiment_score + replies_count + likes_count + retweets_count, ourdata)
summary(lm.mod)
lm.pred <- predict(lm.mod, train_set)
postResample(lm.pred, test_set$teslaDiff.p)
```

