---
title: "Final_Project_Draft"
author: "Jake Peters"
date: "4/20/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(scales)
library(tidytext)
library(textdata)
library(broom)
library(dslabs)
library(stringi)
```

```{r}
df_tweets <- read_csv("https://raw.githubusercontent.com/aksoralis/Data-Mining/main/df_tweets.csv")
stocks <- read_csv("https://raw.githubusercontent.com/aksoralis/Data-Mining/main/stocksdf.csv")
tweets <- df_tweets %>% select(tweet, link, replies_count, likes_count, retweets_count, day)

tweets <- tweets %>% rename(Date = day)
clean <- left_join(tweets,stocks, by= "Date")

clean <- clean %>% 
           filter(Date >= ymd("2017-11-10"))
```


```{r}
clean %>% count(year)

```

```{r}

utf <- clean %>%
    mutate_at(vars(tweet), function(x){gsub('[^ -~]', '', x)})
tweet_words <- utf %>% 
  unnest_tokens(word, tweet, token = "tweets")


```
```{r}
tweet_words %>% 
  count(word) %>%
  arrange(desc(n))
```
taking all stop words out
```{r}
tweet_words <- utf %>% 
  unnest_tokens(word, tweet, token = "tweets") %>%
  filter(!word %in% stop_words$word ) 
```
```{r}

tweet_words %>% 
  count(word) %>%
  top_n(400, n) %>%
  mutate(word = reorder(word, n)) %>%
  arrange(desc(n))
```
tesla words: tesla, @tesla, car, production, @teslarati, cars, engine, @thirdrowtesla, future, power, energy, engines, electric, engineering, autopilot, drive, range, ai, factory, speed, computer, fast, rate, product, battery, control, selfdriving, vehicle, @teslagong, cybertruck, improvements, driving, hardware, testing, data, @teslatruth, gas, @tesmaniancom, reusable, road, fuel, move, mode, vehicles, moving, sustainable, traffic, faster



```{r}
tweet_words_TF <- tweet_words %>% mutate(word_in_tesla = word %in% c("tesla","@teslaownerssv", "@tesla", "car", "production", "@teslarati", "cars", "engine"," @thirdrowtesla", "future", "power", "energy", "engines", "electric", "engineering", "autopilot", "drive", "range", "ai", "factory", "speed", "computer", "fast"," rate", "product", "battery", "control", "selfdriving", "vehicle", "@teslagong", "cybertruck", "improvements", "driving", "hardware", "testing", "data", "@teslatruth", "gas", "@tesmaniancom", "reusable", "road", "fuel", "move", "mode", "vehicles", "moving", "sustainable", "traffic", "faster"))


tfcount <- tweet_words_TF %>% group_by(link) %>% summarize(tesla_score = sum(word_in_tesla)) %>%
  ungroup()

scored <- left_join(utf, tfcount, by = "link")

```

```{r}
write.csv(scored, "C:/Users/13204/Documents/Data Mining/Final_Project/DATA318 Final Project/scored_tesla.csv", row.names = FALSE)
```

